An Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis

### 2021-08-31 paper/paper.tex
update table gen
add percent col to all_samples

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{cite}

@@

\subsection{Dataset}
In order to classify the cuticle, we used ant head images sourced from AntWeb
\cite{antweb}. In general, the ant head images are centered in the image, facing
the front, and share a similar posture. However, some images may not be
centered, show the ant head in a different orientation, or may have a
drastically different resolution from the average image. Additionally, images
can vary in scale. Fortunately, each can have several scales available such that
the images' scales can be roughly similar.

Images were collected and classified by undergraduate students according to the
sculpturing identification protocol. Overall, there are a total of 2443 images
in the dataset. The class spread is shown in

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{cite}
\usepackage{booktabs}

@@

\subsection{Dataset}
In order to classify the cuticle, we used ant head images sourced from AntWeb
\cite{antweb}. In general, the ant head images are centered in the image, facing
the front, and share a similar posture. However, some images may not be
centered, show the ant head in a different orientation, or may have a
drastically different resolution from the average image. Fortunately, each can
have several scales available such that the images' scales can be roughly
similar.

\begin{table}[h]
  \centering
  \caption{Dataset Class Distribution}
  \label{table:classdist}
  \include{tables/all_samples.tex}
\end{table}

Images were collected and classified by undergraduate students according to the
sculpturing identification protocol. Overall, there are a total of 2443 images
in the dataset. The class distribution is shown in Table \ref{table:classdist}.
The relatively small number of images in the dataset paired with the uneven
class distribution makes it difficult to perform a meaningful classification.
However, the goal of this project is to develop a classification algorithm that
can be used to help classify over 200,000 ant images. Therefore, it is desirable
to use a few representative images from each class to train the algorithm.
Additionally, data augmentation and other methods are performed to increase the
number of training images to create a more robust classification algorithm.
